Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}

### 2020-07-02 large_experiment_processing.Rmd
Update large_experiment_processing.Rmd
Co-authored-by: Sebastian Gibb <mail@sebastiangibb.de>

To reproduce the analysis in this document, download the *MSV000080030* folder
from
[ftp://massive.ucsd.edu/MSV000080030/](ftp://massive.ucsd.edu/MSV000080030/) and
place it into the same folder than this document.

>>>>

To reproduce the analysis described in this document, download the *MSV000080030* folder
from
[ftp://massive.ucsd.edu/MSV000080030/](ftp://massive.ucsd.edu/MSV000080030/) and
place it into the same folder as this document.
